M-M paper, morphological bias

### 2015-03-18 papers/MbhMsph/mm.tex
robi<3u

\shorttitle{Data paper}
\shortauthors{Savorgnan et al.}

@@

\title{Data paper}

@@

\begin{abstract}
abstract % 2d worse than 1d say it!!!
\end{abstract}

@@

\section{Introduction}
\label{sec:int}
Supermassive black holes and host bulges have very different sizes. 
If the event horizon of the Galactic supermassive black hole was as big as a grain of sand of the Sahara desert, 
then the black hole gravitational sphere-of-influence would be as big as the international airport of Cairo, 
and the Galactic bulge would be as big as the Sahara desert itself.
It is thus surprising that the masses of supermassive black holes ($M_{\rm BH}$) 
scale with a number of properties of their host bulges, 
indicating the non-gravitational origin of these correlations 
(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,laor1997,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea
that black holes and host galaxies have coevolved with some sort of self-regulated growth.
Exploring the evolution of this growth with cosmic time could help identify
the driving mechanisms of the black hole -- galaxy coevolution.
Observations at $z=0$ set the local benchmark from which to measure this evolution.
Any complete theory or model describing the coevolution of galaxies and black holes must incorporate 
all of the observed scaling relations, which also have to be consistent with each other.
%Modern semi-analytic models use the observed black hole mass scaling relations 
%to constrain the black hole accretion rate .
Modern hydrodynamical simulations, such as EAGLE \citep{schaye2015}, calibrate the feedback efficiencies 
to match the $z=0$ black hole mass -- galaxy mass relation.
Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct
measure of $M_{\rm BH}$ would be extremely time consuming or simply impossible due to technological limitations.
Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 
the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 
and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
All of these examples depend on the $z=0$ relations, 
and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 
has many substantial implications. \\
Since the early stellar dynamical detections of black holes were carried out in the '80s 
(see the references in the reviews by \citealt{kormendyrichstone1995}, \citealt{richstone1998} 
and \citealt{graham2015bulges} for pioneering papers), 
the number of (direct) black hole mass measurements has increased with time 
and it has recently become a statistically meaningful sample  
with which one can study SMBH demographics. 
It is now generally accepted that supermassive black holes reside at the center of most, if not all, 
massive galaxies, either quiescent or active. \\
Massive, early-type galaxies are often composite systems. 
The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
at least three decades  
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 
After examining long-slit and integral field unit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
\cite{donofrio1995}, \cite{graham1998fornax} and \cite{scott2014} concluded that only 3 bright galaxies do not harbour a disk-like component.
Larger surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.
More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.
\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 
In their magnitude-limited survey, systems 
without any signature of disk-like components (neither in the kinematics nor in the photometry) 
dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
if one is to properly explore the black hole-bulge connection. 
Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.
If we are to properly understand the evolution of galaxies, we need to understand their components.\\
Measuring the photometric and structural properties of a galaxy's spheroidal component requires the ability to 
separate it from the rest of the galaxy. 
Such galaxy decomposition involves a parametric analysis that allows one to fit the surface brightness distribution
of galaxies using a combination of analytic functions (usually one function per
galaxy component, such as bulges, disks, bars, nuclei, etc.).
The one-dimensional (1D) technique involves fitting isophotes to the galaxy image, extracting the (one-dimensional) surface 
brightness radial profile and modeling it with a combination of analytic functions.
With the two-dimensional (2D) technique, one fits analytic functions directly to the 2D images. \\
Over the past eight years, five independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal} have attempted galaxy decomposition
in order to derive the bulge parameters and explore their relation with the black hole masses. 
{\bf Rusli has explored the black hole - core relation.}
Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
For example, one study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
whereas the remaining four did not.
In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 
declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.
The past studies did not converge to the same conclusions 
because their best-fit models for the same galaxy were often 
significantly different and not consistent with each other in terms of fitted components. 
Moreover, none of these studies attempted an individual galaxy-by-galaxy 
comparison of their models with the previous literature. 
We have now made this comparison and performed the optimal decompositions,
using $3.6~\rm \mu m$ \emph{Spitzer} satellite imagery, 
which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).
We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
using the largest sample (66) of galaxies to date.

This paper is structured as follows.
Section \ref{sec:data} presents the galaxy sample and imaging data-set used to conduct this study. 
Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
In Section \ref{sec:res} we outline the results from our analysis and discuss the error analysis. 
Section \ref{sec:concl} summarizes our main conclusions. 
The individual galaxy decompositions are made available in the electronic version of this manuscript.

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.

%\clearpage
\input{table_sample.tex}
%\noindent
\input{table_observations.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicking}
We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

\subsubsection{Overlap correction}
Before generating a mosaic, MOPEX can perform background matching among the individual frames
by using the \emph{overlap} module. 
This module calculates and applies an additive correction to the individual frames,
producing a consistent background across the mosaicked image.
According to the \emph{Spitzer Data Cookbook}, the use of the \emph{overlap} module is not particularly recommended for 
$3.6~\rm \mu m$ observations. 
However, after a visual inspection of the mosaics obtained without activating the \emph{overlap} module,
we found that all the mosaics obtained from multiple AORs were affected by patchiness, 
due to bias fluctuations in the CCD array.
For this reason, we re-generated the multiple-AORs mosaics by activating the \emph{overlap} correction,
which successfully removed the ``chessboard'' pattern (see Figure \ref{fig:overlap} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
\caption{Example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

\subsubsection{Sigma mosaics}
For each individual cBCD frame, the IRAC Level 1 pipeline calculates the uncertainty associated to each pixel
and produces an uncertainty frame (or sigma frame).
The initial uncertainty is estimated as the Poisson noise in electrons plus the readout noise added in quadrature
($\sigma^2 = \sigma^2_{\rm readoutnoise} + \sigma^2_{\rm Poisson}$).
This initial sigma frame is carried through the pipeline, and additional uncertainties (e.g.~dark current and flat field uncertainties) 
are added in quadrature when appropriate.
When MOPEX generates an image mosaic, it also produces the associated sigma mosaic 
by interpolating the individual uncertainty frames and co-adding them,
following the standard assumption of additive variances.

\subsubsection{Sky subtraction}
Sky subtraction was performed manually on the image mosaics using the tasks {\tt marksky} and {\tt skyfit} 
of the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} 
package GALPHOT\footnote{GALPHOT was developed in the IRAF - STSDAS environment mainly by 
W. Freudling, J. Salzer, and M. P. Haynes \citep{haynes1999galphot}.}.
The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).
%sky value also checked with Galfit

\subsubsection{Additional aestethic corrections}
\label{sec:aesth}
The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
by bright, highly saturated stars lying close to the target galaxies.
These stars were modeled and subtracted using the software Galfit \citep{peng2010} 
and the extended IRAC Point Response Function (PRF) image at $3.6~\rm \mu m$.
This helped remove the extended wings and spikes of the saturated stars 
(see Figure \ref{fig:aesth} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
\caption{Example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks} that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
globular clusters or red giant stars.

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).

\subsubsection{2D PSF}
The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
we found this PRF to be inadequate for the purposes of our modelling.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

\subsubsection{AGNs and nuclear dust}
The X-ray, UV and optical radiation 
emitted by the the accretion disks of Active Galactic Nuclei (AGNs) can stimulate infrared thermal emission 
from circumnuclear dust, if present. 
This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
we may detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
To help with this task, we searched NED\footnote{NED is the NASA/IPAC Extragalactic Database.} 
for the individual galaxies and their associated literature.
Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies, 
and modelled by us with either a point source or a PSF-convolved Gaussian.

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2013cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was first set to increase linearly, 
and then geometrically in our second run\footnote{In the case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In the case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
equivalent to the circularized radius.
This resulted in 4 profiles per galaxy.
Isophotes corresponding to an intensity less than 
three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.).
Individual cases are discussed in Section \ref{sec:indgal}.

\subsection{Unsharp masking}
Unsharp masking is an image sharpening technique that is useful to reveal asymmetric structures in galaxies, 
such as bars or (inclined) embedded disks. 
First, the original galaxy image was smoothed with a Gaussian filter.
Then, the original image was divided by the smoothed one. 
The result of such an operation is the ``unsharp mask''. 
The asymmetric features revealed by this technique have sizes 
comparable to the $FWHM$ of the Gaussian kernel used for the smoothing.
Therefore, for each galaxy, we produced a set of different unsharp masks by varying the $FWHM$ of the filter,
to identify all the asymmetric features that could bias the fitting process 
and may therefore need to be considered during the galaxy modelling phase.
This information was used in combination with kinematic and AGN information discussed in Section \ref{sec:adddata}.

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked {\bf ??} with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately {\bf ??} 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
and more so than the studies upon which our work is building from,
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

\subsection{Smoothing technique}
\label{sec:smooth}
Some nearby galaxies in our sample have very large apparent sizes 
and for them we obtained surface brightness profiles more extended than $8~\rm arcmin$.
This means that their outermost (significant) isophote 
corresponds to a projected galactic radius $R$ 
of more than $240$ times the $FWHM$ of the instrumental PSF.
Such level of spatial resolution is unnecessary for the purposes of our analysis 
and, especially in the case of a clumpy star forming galaxy, 
it results in a ``noisy'' surface brightness profile.
Moreover, in the case of a linearly sampled light profile,
it significantly prolongs the computational time of the fitting routine 
(because, at each iteration, the PSF convolution is performed numerically on a large array).
To overcome this problem, we introduced a method to which we refer as the ``smoothing technique''.
This method was applied to the galaxies M31, M81, NGC 4945 and NGC 5128.
For each of these galaxies, we took the image mosaic and we convolved it with a Gaussian filter 
whose $FWHM$ was larger than the $FWHM$ of the instrumental PSF.
We then ran {\tt ellipse} on the convolved image and extracted 
``linearly sampled'' and ``logarithmically sampled'' surface brightness profiles. 
For the ``linearly sampled'' profiles, we set the radial step between contiguous isophotes to be 
comparable to the $FWHM$ of the smoothing Gaussian filter.
Doing so, we reduced the number of fitted isophotes and we also produced smoother surface brightness profiles.
Before the software fit a smoothed light profile, the model to be fit was convolved twice:
the first time to account for PSF effects, 
and the second time to account for the artificial Gaussian smoothing applied to the image mosaic.

\subsection{Identifying and modeling sub-components}
\label{sec:cpts}
In this Section we give a general overview of the guidelines that we followed to identify and model 
the sub-components that constitute our galaxies. 
However, given the level of accuracy and detail to which each galaxy decomposition has been performed in our analysis,
it is hard to encompass all aspects of this matter in a few paragraphs.
The modeling of each galaxy represented a particular and original problem, 
and we remand the reader to Section \ref{sec:indgal},
where we provide individual descriptions of the galaxies that we analyzed. \\
As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 
of galaxies.
We assumed \emph{a priori} that each of our galaxies has a unique spheroidal component, 
that we modeled with a S\'ersic profile. \\
Disks were usually fit with the exponential model, 
although in the case of highly inclined or edge-on systems we preferred using an $n < 1$ S\'ersic function. 
\citet{pastrav2013a,pastrav2013b} showed that, due to projection effects, their simulated images of inclined galaxy disks 
are better fit by a S\'ersic function with $n < 1$ than by a pure exponential model.
The inclined, embedded disks of some ``elliptical'' galaxies were described with Ferrer functions, rather than a $n < 1$ S\'ersic function. 
This choice was partly motivated by the fact that a S\'ersic + Ferrer model is less degenerate than a S\'ersic + S\'ersic model, 
since the S\'ersic profile can assume any concave ($n > 1$) or convex ($n < 1$) curvature, 
whereas the Ferrer profile can only have a negative curvature as required for an inclined disk. \\
The presence of large-scale disks, such as those of lenticular and spiral galaxies, 
were known \emph{a priori} from the galaxy morphological classification (as listed on NED), 
although some of them were re-classified by us as having intermediate-scale embedded disks.
These were identified in a number of different ways. 
If highly inclined, they can obviously be spotted from the galaxy image or the unsharp mask.
Local maxima in the ellipticity and fourth harmonic profiles 
can provide footprints of less obvious embedded disks.
In particular, the ellipticity profile helps distinguish embedded disks from large-scale disks.
Galaxy disks typically have fixed ellipticity, reflecting their inclination to our line of sight.
On the other hand, spheroids can have their ellipticities varying with radius,
but they are usually rounder than inclined disks, thus their average ellipticities are lower than those of inclined disks.
If the ellipticity profile of a galaxy increases with radius, 
this can be ascribed to an inclined disk that becomes progressively more important over the spheroid,
whereas a radial decrease of ellipticity signifies the opposite case.
Therefore, in a situation where a disk is identified from the galaxy image, 
but its extent (large- or intermediate-scale) is ambiguous,
the shape of the ellipticity profile can be decisive. 
Another way to establish the presence of an embedded disk is to look at the velocity map of a galaxy,
following the approach of \citet{arnold2014}. 
A local angular momentum decrease with increasing radius is indicative of an intermediate-scale disk 
that fades toward larger radii. \\
%As an illustration, we consider the galaxy NGC 3377.
%For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
%with a disk-to-bulge transition occurring at about $\sim 50''$.
%They did attempt a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
%but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile {\bf TBD: cite de vaucouleurs} 
%rather than a three-parameter $R^{1/n}$ S\'ersic function.
%Here we used a surface brightness profile twice as extended as that used by \citet{arnold2014} 
%and we identified a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component (see Figure \ref{fig:n3377ex}).
%The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
%and also from the ellipticity profile, which increases with increasing radius until $R \sim 45''$ (along the major-axis) 
%and dramatically drops at larger radii.
%The nuclear disk can be spotted from the peak at $R \sim 5''$ in the $B4$ profile.
%In our galaxy model for NGC 3377, 
%the difference between the S\'ersic profile of the bulge and the exponential profile of the intermediate-scale disk is minimum in correspondence 
%of the maximum ellipticity, 
%thus our model correctly reproduces the isophotal properties of the galaxy. 
%The residuals of the fit, especially along the major-axis, display some minor structures which indicate that 
%the bulge S\'ersic index might have been slightly overestimated.
%This could be due to the fact that the embedded disk would be better described by a truncated exponential function.

>>>>

\shorttitle{M-M paper}
\shortauthors{Savorgnan et al.}

@@

\title{M-M paper, morphological bias }

@@

\begin{abstract}
abstract 
\end{abstract}

@@

\section{Introduction}
\label{sec:int}
More than two and a half decades ago, 
\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'', 
as suggested by the sequence of five galaxies (M87, M104, M31, M32 and the Milky Way). 
His ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  
and host spheroid luminosity, $L_{\rm sph}$, and also host spheroid mass, $M_{\rm sph}$ 
\citep{yee1992,kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 
These early studies were dominated by high-mass, early-type galaxies, 
for which they reported a quasi-linear $M_{\rm BH} - M_{\rm sph}$ relation, 
in agreement with a dry-merging formation scenario. 
Subsequent studies of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm sph}$ diagrams 
(\citealt{ferrareseford2005,lauer2007,graham2007,graham2008bar,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,
vika2012,vandenbosch2012,mcconnellma2013,kormendyho2013,rusli2013}; 
see \citealt{graham2015bulges} for an extensive review about the early discovery and successive improvements of these correlations)
used similar galaxy samples, which remained dominated by high-mass, early-type objects having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 
and therefore recovered a near-linear relation. 
However, the consensus about a linear $M_{\rm BH} - M_{\rm sph}$ correlation was not unanimous. 
Some studies reported a slope steeper than 1,  
or noticed that low-mass spheroids were downwards offset from the relation traced by their high-mass counterparts 
\citep{laor1998,wandel1999,laor2001,ryan2007}.

lasker

\section{Data}
\label{sec:data}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}

\section{Analysis}
\label{sec:anal}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}

\section{Results}
\label{sec:res}

\section{Conclusions}
\label{sec:concl}

\acknowledgments
%{\bf marconi, sani, hunt...}
%GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Elisabete Lima Da Cunha and Gonzalo Diaz 
%for useful discussion. \\
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

\bibliography{/Users/gsavorgnan/Dropbox_notsync/giulia_e_basta/Literature/SMBHbibliography}
